---
title: <span style="color:black"><b>Gene set enrichment analysis report</b></span>
params:
  GSEASettings: NA
  GSEATable: NA
  dir: NA
  ArrayAnalysis_version: NA
output:
  html_document:
    includes:
      before_body: header.html
---

<style>
body { background-color: #C6DBEF; }
h1 {
text-align: center;
}
</style>

<p style="color:black; text-align: center">
If you wish to have customized figures, please modify the figures in ArrayAnalysis and download them separately.
</p>

<br>

<div style="background-color:white; padding:1em; border-radius:25px;">
## Settings

```{r, echo=FALSE, results = 'asis'}
GSEASettings <- params$GSEASettings
GSEASettings[1,1] <- "Selected comparison*"
knitr::kable(GSEASettings)
```
<p>*You can generate the report for a different comparison by changing the selected comparison in 
ArrayAnalysis and downloading the report again.</p>
<br>

## Results {.tabset}

### Top hits
<h3><b>Top upregulated gene sets</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
GSEATable <- params$GSEATable@result
knitr::kable(head(GSEATable[GSEATable$NES > 0,], 10), row.names = FALSE)
```

<hr>
<h3><b>Top downregulated gene sets</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
GSEATable <- params$GSEATable@result
knitr::kable(head(GSEATable[GSEATable$NES < 0,], 10), row.names = FALSE)
```

### Bar chart

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeGSEAplot(params$GSEATable,
             nSets = 15,
             color = c("#000072", "white", "red"))
```

### Network

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeGSEAnetwork(GSEA_data = params$GSEATable,
                layout = "graphopt",
                nSets = 15,
                color = c("#000072", "white", "red"),
                size = 3)
```

### Session info

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
params$ArrayAnalysis_version
sessionInfo()
```
</div>