---
title: Gene set enrichment analysis report
params:
  GSEASettings: NA
  GSEATable: NA
---

This report provides an overview of the results from the geneset enrichment analysis (GSEA). If you wish to have customized figures, please modify the figures in ArrayAnalysis and download them separately.

<br>

## Settings

```{r, echo=FALSE, results = 'asis'}
GSEASettings <- params$GSEASettings
GSEASettings[1,1] <- "Selected comparison*"
knitr::kable(GSEASettings)
```
<p>*You can generate the report for a different comparison by changing the selected comparison in 
ArrayAnalysis and downloading the report again.</p>
<br>

## Results {.tabset}

### Top hits
<h3><b>Top upregulated genesets</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
GSEATable <- params$GSEATable@result
knitr::kable(head(GSEATable[GSEATable$NES > 0,], 10), row.names = FALSE)
```

<hr>
<h3><b>Top downregulated genesets</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
GSEATable <- params$GSEATable@result
knitr::kable(head(GSEATable[GSEATable$NES < 0,], 10), row.names = FALSE)
```

### Bar chart

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeGSEAplot(params$GSEATable,
             nSets = 15,
             color = c("#000072", "white", "red"))
```

### Network

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeGSEAnetwork(GSEA_data = params$GSEATable,
                layout = "graphopt",
                nSets = 15,
                color = c("#000072", "white", "red"),
                size = 2)
```

### Session Info

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
sessionInfo()
```