---
title: Overrepresentation analysis report
params:
  ORASettings: NA
  ORATable: NA
---

This report provides an overview of the results from the overrepresentation analysis (ORA). If you wish to have customized figures, please modify the figures in ArrayAnalysis and download them separately.

<br>

## Settings

```{r, echo=FALSE, results = 'asis'}
ORASettings <- params$ORASettings
ORASettings[1,1] <- "Selected comparison*"
knitr::kable(ORASettings)
```
<p>*You can generate the report for a different comparison by changing the selected comparison in 
ArrayAnalysis and downloading the report again.</p>
<br>

## Results {.tabset}

### Top hits
<h3><b>Top overrepresented genesets</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
ORATable <- params$ORATable@result
knitr::kable(head(ORATable, 15), row.names = FALSE)
```

### Bar chart

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeORAplot(params$ORATable,
            nSets = 15,
            color = "Viridis")
```

### Network

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeORAnetwork(ORA_data = params$ORATable,
               layout = "graphopt",
               nSets = 15,
               color = "Viridis",
               size = 2)
```
