---
title: <span style="color:black"><b>Quality control report</b></span>
params:
  processingSettings: NA
  experimentFactor: NA
  legendColors: NA
  normData: NA
  normMatrix: NA
  PCAData: NA
  dir: NA
  ArrayAnalysis_version: NA
output:
  html_document:
    includes:
      before_body: header.html
---

<style>
body { background-color: #C6DBEF; }
h1 {
text-align: center;
}
</style>

<p style="color:black; text-align: center">
If you wish to have customized figures, please modify the figures in ArrayAnalysis and download them separately.
</p>

<br>

<div style="background-color:white; padding:1em; border-radius:25px;">
## Settings

```{r, echo=FALSE, results = 'asis'}
knitr::kable(params$processingSettings)
```

<br>

## Results {.tabset}

### Boxplot
<h3 style="text-align: center;"><b>Boxplot of normalized intensities</b></h3>
<h5 style="text-align: center;">Distributions should be comparable between samples</h5>
<hr>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
knitr::include_graphics(
  getBoxplots(experimentFactor = params$experimentFactor,
            legendColors = params$legendColors,
            normData = params$normData,
            RNASeq = FALSE,
            width = 1000,
            height = 1414)$src
)
```

### Density plot
<h3 style="text-align: center;"><b>Density plot of normalized intensities</b></h3>
<h5 style="text-align: center;">Distributions should be comparable between samples</h5>
<hr>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
getDensityplots(experimentFactor = params$experimentFactor,
                legendColors = params$legendColors,
                normMatrix = params$normMatrix,
                RNASeq = FALSE)
```

### Correlation plot
<h3 style="text-align: center;"><b>Heatmap of sample-sample correlations</b></h3>
<h5 style="text-align: center;">Constructed using Pearson correlation and Ward D2 linkage method</h5>
<hr>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
legendColors <- params$legendColors
names(legendColors) <- levels(params$experimentFactor)
getHeatmap(experimentFactor = params$experimentFactor,
           legendColors = legendColors,
           normMatrix = params$normMatrix,
           clusterOption1 = "Pearson",
           clusterOption2 = "ward.D2",
           theme = "Default")
```

### PCA plot
<h3 style="text-align: center;"><b>Scatter plot of PCA scores</b></h3>
<h5 style="text-align: center;">Samples with similar expression profiles are close to each other</h5>
<hr>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
plot_PCA(PC_data = params$PCAData, 
         colorFactor = params$experimentFactor,
         legendColors = params$legendColors, 
         xpc = 1, 
         ypc = 2, 
         zpc = NULL, 
         xyz = FALSE)
```

### Session info

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
params$ArrayAnalysis_version
sessionInfo()
```
</div>