---
title: Statistical analysis report
params:
  statSettings: NA
  topTable: NA
  volcanoTable: NA
---

This report provides an overview of the results from the statistical analysis. If you wish to have customized figures, please modify the figures in ArrayAnalysis and download them separately.

<br>

## Settings

```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
statSettings <- params$statSettings
statSettings[1,1] <- "Selected Comparison*"
knitr::kable(statSettings)
```
<p>*You can generate the report for a different comparison by changing the selected comparison in 
ArrayAnalysis and downloading the report again.</p>
<br>

## Results {.tabset}

### Top hits
<h3><b>Top upregulated genes</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
topTable <- params$topTable
knitr::kable(head(topTable[topTable$log2FC > 0,], 10), row.names = FALSE)
```

<hr>
<h3><b>Top downregulated genes</b></h3>
```{r, echo=FALSE, results = 'asis', message = FALSE, warning = FALSE}
topTable <- params$topTable
knitr::kable(head(topTable[topTable$log2FC < 0,], 10), row.names = FALSE)
```

### Histograms

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makePHistogram(params$topTable[,"p-value"])
```
<hr>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makelogFCHistogram(params$topTable[,"log2FC"])
```

### Volcano plot

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeVolcano(top_table = params$topTable, 
            p = "raw", 
            p_threshold = 0.05, 
            logFC_threshold = 1)
```

<br>
<h4># genes per p-value and logFC category</h4>
```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
knitr::kable(params$volcanoTable)
```

### MA plot

```{r, echo=FALSE, out.width="100%", out.height = "100%", message = FALSE, warning = FALSE}
makeMAplot(top_table = params$topTable, 
           p = "raw", 
           p_threshold = 0.05, 
           logFC_threshold = 1)
```
